{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-05-24 thesis/education.tex
test cases

@@

@@

% mx, bcast, paradise, paraguay, rwl dgr, exit join

% for psu additionally - bcast test 2, and all the atomics

>>>>

\subsection{Recruiting}
\label{sec:education-pebbles-recruiting}

@@

\subsection{Automatic instrumentation}
\label{sec:education-pebbles-instrumentation}

@@

Landslide ships with several ``approved'' test cases,
i.e., programs copied from, derived from, or at least vaguely resembling
the tests distributed with P2,
which I curated to produce concurrent behaviour suitable for stateless model checking.
Some tests are crafted to target specific bugs which,
from personal experience as a TA, are common in many student submissions;
others are crafted to exercise generally concurrency-heavy code paths and uncover any number of unforeseen problems.

The following tests were released to CMU students:
\begin{itemize}
	\item {\tt broadcast\_test}:
		Tests the {\tt cond\_broadcast()} signalling path with a single waiter.
	\item {\tt mutex\_test}:
		Tests student mutexes under 2 threads with 2 iterations
		(the 2nd iteration serves to expose problems with {\tt mutex\_unlock()} as well as {\tt mutex\_lock()}).
		This test uses the special {\tt TESTING\_MUTEXES} data-race analysis mode
		described in \sect{\ref{sec:landslide-staticconfig}}.
	\item {\tt paradise\_lost}:
		Written for the sake of the Landslide lecture demo
		(\sect{\ref{sec:education-pebbles-recruiting}}).
		Tests for the Paradise Lost bug by attempting to break mutual exclusion.
	\item {\tt paraguay}:
		Copied directly from the P2 test suite;
		tests for proper handling of seemingly ``spurious'' wakeups in {\tt cond\_wait()}.
		Written by Michael Sullivan.
	\item {\tt rwlock\_downgrade\_read\_test}:
		Copied directly from the P2 test suite;
		tests for mutually-exclusive and deadlock-free {\tt rwlock\_downgrade()}.
		Written by me (as a TA).
	\item {\tt thr\_exit\_join}:
		Copied directly from the P2 test suite;
		tests for a variety of problems between {\tt thr\_exit()} and {\tt thr\_join()},
		but especially for memory issues pertaining to stack deallocation.
\end{itemize}
The following tests were released to PSU students, in addition to the ones above:
\begin{itemize}
	\item {\tt atomic\_compare\_swap}:
		Tests the {\tt cmpxchg} assembly function for being properly atomic.
		Uses the {\tt magic\_*} global variables, and invokes {\tt vanish()} directly,
		to avoid requiring the student to implement {\tt thr\_join()}/{\tt thr\_exit()}
		before being able to run this test.
	\item {\tt atomic\_exchange}:
		As above for {\tt xchg}.
	\item {\tt atomic\_fetch\_add}:
		As above for {\tt xadd}.
	\item {\tt atomic\_fetch\_sub}:
		As above for {\tt xadd}.
	\item {\tt broadcast\_two\_waiters}:
		As {\tt broadcast\_test}, but uses two waiting threads to ensure both get signalled.
\end{itemize}
